\documentclass[11pt,a4paper]{article}

% Packages
\usepackage[margin=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{parskip}

% Colors
\definecolor{linkblue}{HTML}{0645AD}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=linkblue,
    urlcolor=linkblue,
}

% Section formatting
\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{6pt}

% Subsection formatting
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}

% Remove page numbers (optional, comment out to keep them)
% \pagestyle{empty}

% Custom commands
\newcommand{\entrytitle}[1]{\textbf{#1}}
\newcommand{\entrydetail}[1]{\textit{#1}}

\begin{document}

%---------- HEADER ----------
\begin{center}
    {\LARGE\textsc{Xiayu Zhao}} \\[6pt]
    PhD Student \,|\, Robotic, Automation, and Intelligent Sensing (RAISe) Lab \\
    University of Illinois Urbana-Champaign (UIUC) \\
    Civil and Environmental Engineering -- The Grainger College of Engineering \\
    205 N Mathews Ave, Urbana, IL 61801 \\[4pt]
    Phone: (582)\,203-0776 \quad|\quad Email: \href{mailto:xiayuz3@illinois.edu}{xiayuz3@illinois.edu} \quad|\quad Web: \href{http://www.raiseclab.com}{www.raiseclab.com}
    \\[4pt]
    {\small Last updated: \today}
\end{center}

%---------- RESEARCH INTERESTS ----------
\section{Research Interests}

AI and machine learning algorithms for seamless human-robot collaboration; Computer vision techniques for automated inspection tasks; Construction robotics; Robotic control and navigation.

%---------- EDUCATION ----------
\section{Education}

\entrytitle{Ph.D. Student}, \entrydetail{Civil and Environmental Engineering, The Grainger College of Engineering, University of Illinois Urbana-Champaign} \hfill Spring 2024 -- present \\[-1.5em]
\begin{itemize}[nosep, leftmargin=1.5em]
    \item Advisor: Dr.\ Houtan Jebelli
    \item GPA: 3.91/4.00 (Spring 2024 -- present)
    \item Dissertation Title: 
\end{itemize}

\entrytitle{Master of Computer Science}, \entrydetail{Siebel School of Computing and Data Science, University of Illinois Urbana-Champaign} \hfill 2025 -- 2027 \\[-1.5em]
\begin{itemize}[nosep, leftmargin=1.5em]
    \item Research fields: Vision, Graphics, Interaction, and Robotics.
    \item GPA: 4.00/4.00 (Fall 2025 -- present)
    \item Courses taken: CS598 (Deep Learning for Robotic Manipulation) A, CS547/IE534 (Deep Learning) A+, ECE470 (Introduction to Robotics) A, CS598 (Advanced Computational Topics in Robotics) A-, CS443 (Reinforcement Learning) B+, Ordered Data Structures (Coursera, provided by UIUC), Object-Oriented Data Structures in C++ (Coursera, provided by UIUC).
\end{itemize}

\entrytitle{Master of Architecture}, \entrydetail{Tsinghua University, Beijing, China} \hfill 2019 -- 2021 \\[-1.5em]
\begin{itemize}[nosep, leftmargin=1.5em]
    \item Research fields: Robotic Construction, 3D Printing, Computational Design, GPA: 3.97/4.00
\end{itemize}

\entrytitle{Bachelor of Architecture}, \entrydetail{Tianjin University, Tianjin, China} \hfill 2014 -- 2019 \\[-1.5em]
\begin{itemize}[nosep, leftmargin=1.5em]
    \item Research fields: Computational Design, GPA: 3.85/4.00
\end{itemize}

%---------- ACADEMIC APPOINTMENTS ----------
\section{Academic Appointments}

\entrytitle{Graduate Student Research Assistant}, \entrydetail{University of Illinois Urbana-Champaign, Urbana, IL, U.S.} \hfill Spring 2024 -- present \\
Supervisor: Professor Houtan Jebelli

\entrytitle{Graduate Student}, \entrydetail{Icon Lab, Penn State University} \hfill Fall 2023 \\
\entrydetail{Robotic Construction Safety Training Prototype with Immersive Technology (VR)} \\
Role: \textbf{Team Leader} \,|\, Supervisor: Professor John Messner \,|\, TA: Saleh Alghamdi \\
Team: Tessa Beauchat, Islam Gharaibeh, Fangxiao Li
\begin{itemize}[nosep, leftmargin=1.5em]
    \item Connected ROS (Robot Operating System) with Unity 3D to control robot arm mounted UGV (Unmanned Ground Vehicle) in immersive simulation environments.
    \item Developed an interactive, game-based prototype specifically for collision-avoidance safety training, targeted at workers involved in human-robot collaborative construction scenarios.
\end{itemize}

\entrytitle{Research Assistant}, \entrydetail{DAIC (Digital Architecture and Robotic Construction) Lab, Tsinghua University} \hfill Jul.\ 2021 -- Apr.\ 2023 \\
Supervisor: Professor Weiguo Xu
\begin{itemize}[nosep, leftmargin=1.5em]
    \item Extracted design information to program and control robot arms for large-scale 3D printing.
    \item Developed software plug-ins for robotic construction, including 3D printing, metal cutting, wood cutting, wall painting, etc.
\end{itemize}

\entrytitle{Master's Thesis and Graduation Design} \hfill Spring 2021 \\
\entrydetail{Large-Scale Multi-Robots 3D Printing Construction Planning} \,|\, Instructor: Professor Weiguo Xu

\entrytitle{Student Assistant}, \entrydetail{Built Environmental Virtual Reality Lab, Tianjin University} \hfill 2016 -- 2017 \\
Instructor: Professor Sinan Yuan \\
Sponsor: \entrydetail{National Natural Science Foundation}
\begin{itemize}[nosep, leftmargin=1.5em]
    \item Related Methods: Field research, Data Collection, 3D Modeling, Data Input, Data Visualization using a Game Engine, VR Experience for Volunteers, Analysis of Statistical Results, Spatial morphology, and Human Spatial Cognition Mechanisms.
\end{itemize}

%---------- TEACHING AND MENTORING ----------
\section{Teaching and Mentoring}

\entrytitle{Teaching Assistant}, \entrydetail{Robotic Construction Research Series, Robotic Construction Group, Tsinghua University} \hfill Sep.\ 2022 -- Apr.\ 2023 \\
Supervisor: Professor Weiguo Xu
\begin{itemize}[nosep, leftmargin=1.5em]
    \item Advising master students with their graduation projects related to robotic construction.
    \item Research topics involved plastic 3D printing, wood cutting, and foam cutting with KUKA robot arm.
\end{itemize}

\entrytitle{Teaching Assistant}, \entrydetail{Tsinghua University Parametric Design Workshop 2019} \hfill Jul.\ 2019 \\
Tutor: Casey Rehm \\
Project Title: \entrydetail{Artificial Intelligence Architectural Design -- 2D and 3D Generative Neural Network Techniques for Design Biomorphism.}

\entrytitle{Teaching Assistant}, \entrydetail{Computer-Aided Architectural Design Research in Asia (CAADRIA) Workshop 2018} \hfill May 2018 \\
Tutors: Shajay Bhooshan, Vishu Bhooshan, Henry Louth, Leo Claudius \\
Project Title: \entrydetail{Developable Funicular Skeletons with Tensioning Membranes}

%---------- PROFESSIONAL EXPERIENCES ----------
\section{Professional Experiences}

\entrytitle{Research Engineer}, \entrydetail{Institute of Future Human Habitats} \hfill 2021 -- 2023 \\
\entrydetail{Tsinghua University Shenzhen International Graduate School (SIGS)}
\begin{itemize}[nosep, leftmargin=1.5em]
    \item Developed large-scale robotic construction technology based on composite consumables and practical building materials with an interdisciplinary team.
    \item Developed software interface to streamline input and control.
\end{itemize}

\entrytitle{3D Concrete Printing Specialist}, \entrydetail{Heqing Digital Building Technology Co.} \hfill 2020 -- Apr.\ 2023
\begin{itemize}[nosep, leftmargin=1.5em]
    \item Participated in several on-site robotic construction projects in China and the US, including designing the shape, designing the print path, writing the print program, operating the robot arm on-site, post-maintenance, etc.
\end{itemize}

\entrytitle{Intern Architect}, \entrydetail{Zaha Hadid Architects} \hfill Jun.\ -- Sept.\ 2020 \\
Project Director: Satoshi Ohashi
\begin{itemize}[nosep, leftmargin=1.5em]
    \item Participated in the design stage of the final winning bid -- competition -- design of \textit{Tower C of Shenzhen Bay Super Headquarters}.
    \item Participated in the Preliminary design of the Unicorn Island project in Sichuan.
\end{itemize}

\entrytitle{Intern Architect}, \entrydetail{China Architecture Design \& Research Institute} \hfill Jun.\ -- Sept.\ 2018 \\
Project Director: Professor Xinggang Li
\begin{itemize}[nosep, leftmargin=1.5em]
    \item Participated in the design of the \textit{National Sliding Center} in the Beijing 2022 Winter Olympic Games in the Yanqing District.
\end{itemize}


\entrytitle{Co-designer}, \entrydetail{Model Slicing and Toolpath Plug-in Development for Robotic Construction} \hfill Mar.\ -- Apr.\ 2023 \\
Project Leaders: Chenwei Sun, Weiguo Xu

\entrytitle{Principal Designer}, \entrydetail{Rotatable Fine Extrusion Print Head Design for 3DCP Decorative Panels} \hfill Oct.\ 2021 -- Feb.\ 2022 \\
Partners: Zilu Guo, Qi Liu, Chenwei Sun

\entrytitle{Associate Project Manager}, \entrydetail{Wooden House Renovation with Multi-Robots 3D Printed Walls} \hfill Jul.\ -- Aug.\ 2022 \\
Project Leaders: Weiguo Xu, Chenwei Sun \\
Sponsor and Co-designer: University of Hong Kong, Prof.\ Lin John C.H.

\entrytitle{Principal Designer}, \entrydetail{Factory Fa\c{c}ade Design Based on Style Transfer Machine Learning} \hfill 2022 \\
Zhangjiakou, Hebei, China

\entrytitle{Lead Designer}, \entrydetail{Robot 3D Concrete Printed Model House for Low-income People in Africa} \hfill 2020 \\
Project Leader: Weiguo Xu \,|\, Wuxi, Zhejiang, China

\entrytitle{Designer and Engineer}, \entrydetail{Wujiazhuang Multi-Robots 3D Concrete Printed Farmhouse} \hfill 2020 \\
Project Leaders: Weiguo Xu, Yuan Gao, Chenwei Sun \,|\, Wujiazhuang, Hebei, China

%---------- AWARDS & HONORS ----------
\section{Awards \& Honors}

\subsection*{Academic Awards}
\begin{itemize}[nosep, leftmargin=1.5em]
    \item \entrytitle{Olympiad Medalist} -- All Engineering Field, 2025 Olympiad in Engineering Science \hfill 2025 \\
    Held at the University of Stavanger, Norway \\
    Submission: \entrydetail{Autonomous Drone-based System for Precision, Non-contact Surface Finishing in Construction} \\
    Team: Tianyu Ren, Xiayu Zhao, Houtan Jebelli
    \item \entrytitle{First Place} -- ASCE 2025 Global Robotics and Automation Competition \hfill 2025 \\
    2025 ASCE Computing Conference, New Orleans, hosted by the ASCE Computing Division \\
    Submission: \entrydetail{Module-enhanced Slope-Adaptive and Hazard-Aware Hexapod Robotic System for Safe Roof Inspection} \\
    Team: Xiayu Zhao, Houtan Jebelli
    \item \entrytitle{Journal Cover Feature} -- \entrydetail{Computer-Aided Civil and Infrastructure Engineering} \hfill 2025 \\
    Paper: \entrydetail{A Computational Method for Real-time Roof Defect Segmentation in Robotic Inspection}
    \item \entrytitle{Outstanding Graduate Award} \hfill 2019
    \item \entrytitle{Outstanding Graduation Design Award} \hfill 2019
    \item \entrytitle{Tianjin University's Outstanding Student Award} (1/1000) \hfill 2019
    \item \entrytitle{Outstanding Project Assignment in National Higher Education Institutions} \hfill 2017
    \item \entrytitle{Honorable Mention} -- Skyscraper Competition (eVolo) \hfill 2018 \\
    Team: Jiangchen Hu, Yining Bei, Mingwen Zhang
    \item \entrytitle{China Architecture Newcomers Competition -- Top 100 Award} \hfill 2017
    \item \entrytitle{4\textsuperscript{th} National Tournament of Green Building Innovation (2015) -- First Prize} \hfill 2015 \\
    Team: Adela Wei, Mark Wang, Mason Yang, Yu Zhao \\
    Sponsor: \entrydetail{The Chartered Institute of Building (CIOB)}
\end{itemize}

\subsection*{Academic Scholarship}
\begin{itemize}[nosep, leftmargin=1.5em]
    \item \entrytitle{University Graduate Fellowship} (Sponsor: \entrydetail{Pennsylvania State University}) \hfill 2023
    \item \entrytitle{College of Engineering Scholarship} (Sponsor: \entrydetail{College of Engineering, PSU}) \hfill 2023
    \item \entrytitle{China National Scholarship} (1/101) \hfill 2018
    \item \entrytitle{China National Scholarship} (1/97) \hfill 2016
    \item \entrytitle{China National Scholarship} (1/94) \hfill 2015 \\
    (Sponsor: \entrydetail{Ministry of Education of the People's Republic of China})
\end{itemize}

%---------- PUBLICATIONS ----------
\section{Publications}

\subsection*{Refereed Journal Papers}
\begin{enumerate}[leftmargin=1.5em]
    \item \textbf{Zhao, X.} and Jebelli, H. (2025). ``A Computational Method for Real-time Roof Defect Segmentation in Robotic Inspection.'' \textit{Computer-Aided Civil and Infrastructure Engineering}, 1--28. (Featured as the cover image of the journal.)

    \item \textbf{Zhao, X.}, Liu, Y., and Jebelli, H. (2025). ``Module-Enhanced Slope-Adaptive and Hazard-Aware Hexapod Robotic System for Safe Roof Inspection.'' \textit{ASCE OPEN: Multidisciplinary Journal of Civil Engineering}, 3(1), 04025011.

    \item Ye, W., Chen, S., \textbf{Zhao, X.}, Xu, W. (2022). ``Porous Space --- Biomimetic of Tafoni in Computational Design.'' \textit{Architectural Intelligence}. 18 (2022).

    \item \textbf{Zhao, X.}, Xu, W. (2021). ``Research Progress and Application Status of 3D Printing Construction Technology.'' \textit{Chinese \& Overseas Architecture}. 10(2021):7--13.
\end{enumerate}

\subsection*{Journal Manuscripts in Progress}

% Placeholder: Add journal manuscripts in progress here as they become available.
\textit{To be updated.}

\subsection*{Refereed Conference Papers}
\begin{enumerate}[leftmargin=1.5em, resume]
    \item Ren, T., \textbf{Zhao, X.}, and Jebelli, H. (2026). ``Dynamic Robotic Control Strategies for UAV Stability with Rotatory Payload.'' (Accepted).

    \item \textbf{Zhao, X.}, Ren, T., and Jebelli, H. (2026). ``LLM-Driven Safe Robotic Navigation in Construction Sites: A Prompt Engineering Framework with Terrain-Adaptive Path Planning.'' (Accepted).

    \item \textbf{Zhao, X.}, Liu, Y., and Jebelli, H. (2026). ``Hybrid UAV-UGV System with Interchangeable Ground Modules for Multi-Terrain Construction Site Inspection.'' (Accepted).

    \item Guo, X., Li, Y., Kong, X., Jiang, Y., \textbf{Zhao, X.}, Gong, Z., Zhang, Y., et al. (2025). ``Toward Engineering AGI: Benchmarking the Engineering Design Capabilities of LLMs.'' \textit{NeurIPS 2025 Datasets and Benchmarks Track}. arXiv:2509.16204.

    \item \textbf{Zhao, X.} and Jebelli, H. (2025). ``Adaptive Kinematic and Dynamic Control for Hexapod Robots in Complex Construction Environments.'' \textit{Proceedings of the 42nd International Symposium on Automation and Robotics in Construction (ISARC 2025)}, Montreal, Canada, pp.\ 210--217. \href{https://doi.org/10.22260/ISARC2025/0029}{https://doi.org/10.22260/ISARC2025/0029}.

    \item \textbf{Zhao, X.}, Ren, T., Liu, Y., and Jebelli, H. (2025). ``Sensor Fusion and Hierarchical Inspection Strategy for Aerial-Ground Multi-Robot System.'' \textit{Proceedings of the 42nd International Symposium on Automation and Robotics in Construction (ISARC 2025)}, Montreal, Canada, pp.\ 163--170.

    \item Ren, T., \textbf{Zhao, X.}, and Jebelli, H. (2025). ``Advanced Sensor Integration for Enhanced Flight Control in UAV-Based Construction Automation.'' \textit{Proceedings of the 42nd International Symposium on Automation and Robotics in Construction (ISARC 2025)}, Montreal, Canada, pp.\ 122--129.

    \item Liu, J., Ping, Y., Wang, Y., and \textbf{Zhao, X.} (2025). ``Machine Learning-Based Optimization for Modular Robotic Systems in Construction: A Review.'' \textit{2025 International Conference on Computing in Civil Engineering (i3CE)}. (Accepted).

    \item \textbf{Zhao, X.}, Ren, T., and Jebelli, H. (2024). ``Adaptive Intelligence for Robot Navigation Efficiency with a Deep-Reinforcement-Learning-Based Cyber-Physical System.'' \textit{2024 International Conference on Computing in Civil Engineering (i3CE)}, Pittsburgh, Pennsylvania, U.S. (Accepted).

    \item \textbf{Zhao, X.}, and Jebelli, H. (2024). ``Grounding Large Language Models in Robot Control: Facilitating Human-Robot Collaboration in Construction.'' \textit{2024 International Conference on Computing in Civil Engineering (i3CE)}, Pittsburgh, Pennsylvania, U.S. (Accepted).

    \item Ojha, A., \textbf{Zhao, X.}, Zhang, Y., Liu, Y., and Jebelli, H. (2024). ``Improving Heat Strain Prediction in Construction Workers: A Transfer Learning Approach to Overcome Variability Challenges.'' \textit{2024 International Conference on Computing in Civil Engineering (i3CE)}, Pittsburgh, Pennsylvania, U.S. (Accepted).

    \item Ojha, A., Gautam, Y., \textbf{Zhao, X.}, Sharifironizi, A., Jebelli, H., and Martin, A. (2024). ``Understanding the Impact of an Exoskeleton System On Metabolic Cost of Workers During Common Repetitive Construction Tasks.'' \textit{2024 International Conference on Computing in Civil Engineering (i3CE)}, Pittsburgh, Pennsylvania, U.S. (Accepted).

    \item \textbf{Zhao, X.}, Xu, Z., Xu, W. (2023). ``Reusable Assembled Lightweight 3D Concrete Printed Components Based on Tessellation Patterns.'' \textit{IASS Symposium 2023}. (Abstract Accepted).

    \item Ye, W., \textbf{Zhao, X.}, Xu, W. (2022). ``Simulation Algorithm Based on Weathered Rock Morphology and Optimization Algorithm for Design Applications.'' in \textit{Hybrid Intelligence: Proceedings of the 4\textsuperscript{th} International Conference on Computational Design and Robotic Fabrication (CDRF 2022)}. Online and Global, 2022.
\end{enumerate}

\subsection*{Poster Presentations}

% Placeholder: Add poster presentations here as they become available.
\textit{To be updated.}

%---------- INVITED INTERVIEWS, EXHIBITIONS AND SPEECHES ----------
\section{Invited Interviews, Exhibitions and Speeches}

\subsection*{Exhibitions and Invited Speeches}

\entrytitle{Bi-City Biennale of Urbanism/Architecture 2022} \hfill Apr.\ 2022 -- Jan.\ 2023 \\
Title: \entrydetail{Assembled 3D Printed Concrete Urban Miniature Garden} \\
Role: \textbf{Lead Exhibit Designer} \,|\, \entrydetail{Kingway Brewery}, Shenzhen, Guangdong, China

\entrytitle{Design as Solution: Shenzhen Design Week 2021} \hfill Dec.\ 2021 \\
Title: \entrydetail{Robotic 3D Printed Concrete Construction Works} \\
Role: \textbf{Keynote Speaker \& Lead Exhibit Designer} \,|\, \entrydetail{UpperHills}, Shenzhen, Guangdong, China

\entrytitle{Future-Home: Beijing Urban Architecture Biennale 2021} \hfill Oct.\ 2021 \\
Role: \textbf{Exhibit Designer} \,|\, \entrydetail{Zhangjiawan Design Town}, Beijing Urban Vice Center

\subsection*{Invited Interviews}

% Placeholder: Add invited interviews here as they become available.
\textit{To be updated.}

%---------- SERVICE ACTIVITIES & PROFESSIONAL LEADERSHIP ----------
\section{Professional Leadership \& Service Activities }

\subsection*{Professional Committees}

% Placeholder: Add professional committee memberships here as they become available.
\textit{To be updated.}

\subsection*{Journal \& Conference Reviewer (Selected)}

\textit{Journal Reviewer}
\begin{itemize}[nosep, leftmargin=1.5em]
    \item Developments in the Built Environment
    \item ASCE Open Journal
\end{itemize}

\textit{Conference Reviewer}
\begin{itemize}[nosep, leftmargin=1.5em]
    \item ASCE International Conference on Computing in Civil Engineering (i3CE 2024)
    \item ASCE International Conference on Computing in Civil Engineering (i3CE 2025)
    \item ASCE International Conference on Computing in Civil Engineering (i3CE 2026)
    \item 42nd International Symposium on Automation and Robotics in Construction (ISARC 2025)
    \item 43rd International Symposium on Automation and Robotics in Construction (ISARC 2026)
    \item 12th International Conference on Industrial Ecology (ISIE 2025)
    \item CI \& CRC 2026 Joint Conference
\end{itemize}



\entrytitle{Student Member}, American Society of Civil Engineers (ASCE) \hfill Fall 2023 -- present


\entrytitle{Cat Foster Volunteer}, Vermilion County Animal Shelter \hfill 2025 -- present

\entrytitle{Team Leader}, Data Forum Center, Tsinghua University Student Union \hfill Fall 2020 \\
Job Contents: Campus Applet Development; Data Visualization.

\entrytitle{Activity Manager}, Sports Department of Graduate Student Union, Tsinghua University \hfill Fall 2019

\entrytitle{Event Organizer}, Purple (LGBTQ+ Community), Tsinghua University \hfill Fall 2019 -- Spring 2021

\entrytitle{Team Member}, Women's Soccer Team, School of Architecture, Tsinghua University \hfill 2019 -- 2020

%---------- COMPUTER SKILLS ----------
\section{Computer Skills}

\textbf{Robot Programming/OS:} ROS, Industrial Robot Language (URScript), C\# \\
\textbf{Programming:} Matlab, Python, R, C++ \\
\textbf{Simulation Software:} Unity, Unreal Engine \\
\textbf{Statistical Analysis Software:} IBM-SPSS \\
\textbf{Drawing and Building Information Modeling:} AutoCAD, Revit, Rhino, Grasshopper, Sketch-Up, SolidWorks, Adobe Photoshop, Adobe Illustrator \\
\textbf{General Software/Platform:} MS-Office, \LaTeX, Google Colab, Jupyter Notebook

%---------- REFERENCES ----------
\section{References}

Available upon request.

\end{document}
